D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-14 ootavacuous.tex
compilers: Add roadmap
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@@ Fill in roadmap when sectioning is finalized.

>>>>

Section~\ref{sec:Users Influence the Behavior of Compilers}
shows that C++ compilers can be influenced by their users as well
as by the standard.
Section~\ref{sec:Global Optimization Can Destroy Dependencies}
presents an example showing that global optimizations can destroy
semantic dependencies, and then
Section~\ref{sec:Inventing Atomic Loads Can Destroy Semantic Dependencies}
analyzes examples showing that inventing atomic loads can destroy
semantic dependencies.
Section~\ref{sec:Volatile and Quasi Volatile Accesses}
then presents required properties of volatile atomic operations, and
also defines quasi-volatile properties for non-volatile atomic operations.
